|

### 2021-08-07 prova_knit_finale.Rmd
altri x/2

```{r include=FALSE}
# Simulating the data
# -------------------
set.seed(12345)
n     =  50
alpha =  0
beta  =  0.99
tau2  =  0.05
tau   = sqrt(tau2)
y     = rep(0,n)
x     = rep(0,n)
x[1]  = alpha/(1-beta)
y[1]  = rnorm(1,0,exp(x[1]))
for (t in 2:n){
  x[t] = alpha + beta*x[t-1] + rnorm(1,0,tau)
  y[t] = rnorm(1,0,exp(x[t]))
}
alpha.true = alpha
beta.true  = beta
tau2.true  = tau2

>>>>

```{r include=FALSE}
# Simulating the data
# -------------------
set.seed(12345)
n     =  50
alpha =  0
beta  =  0.99
tau2  =  0.05
tau   = sqrt(tau2)
y     = rep(0,n)
x     = rep(0,n)
x[1]  = alpha/(1-beta)
y[1]  = rnorm(1,0,exp(x[1]/2))
for (t in 2:n){
  x[t] = alpha + beta*x[t-1] + rnorm(1,0,tau)
  y[t] = rnorm(1,0,exp(x[t]/2))
}
alpha.true = alpha
beta.true  = beta
tau2.true  = tau2
